Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-12-11 revision.tex
removed noisy rendering figure and included a paragraph about the challenges in the introduction

The new contributions of this work are:
(1) A model that converts sketches to high-level programs:
in contrast to converting images to vectors or low-level parses~\citep{huang2017shape,Nishida:2016:ISU:2897824.2925951,nsd,DBLP:journals/corr/Beltramelli17,im2latex}.
(2) An algorithm for learning a policy for efficiently searching for programs,
building on Levin search~\citep{levin1973universal}
and recent work like DeepCoder~\citep{BalGauBroetal16}.
(3) The trace hypothesis: a framework for going from perception to programs,
which connects this work to other models of program induction that use traces,
like the  Neural Program Interpreter~\citep{DBLP:journals/corr/ReedF15}.

@@

\subsection{Generalizing to real hand drawings}\label{generalizingTheHandDrawings}
\begin{wrapfigure}{R}{6cm}
\centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
    \subcaption{}
  \end{minipage}\\
   \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
    \subcaption{}
  \end{minipage}%
    \caption{(a): hand drawing. (b): Rendering of the trace set our model infers for (a). (c): noisy rendering of (b).}\label{handDrawingExamples}
\end{wrapfigure}

%A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
 We trained the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images.
We designed this noise process to introduce the kinds of variations found in hand drawings (Fig.~\ref{handDrawingExamples}; see supplement for details).

>>>>

The new contributions of this work are:
(1) A model that converts sketches to high-level programs:
in contrast to converting images to vectors or low-level parses~\citep{huang2017shape,Nishida:2016:ISU:2897824.2925951,nsd,DBLP:journals/corr/Beltramelli17,im2latex}.
(2) An algorithm for learning a policy for efficiently searching for programs,
building on Levin search~\citep{levin1973universal}
and recent work like DeepCoder~\citep{BalGauBroetal16}.
(3) The trace hypothesis: a framework for going from perception to programs,
which connects this work to other trace--based models,
like the  Neural Program Interpreter~\citep{DBLP:journals/corr/ReedF15}.

Even with the high-level idea of a trace set, going from hand drawings to programs remains difficult. We address the following challenges:
(1) Inferring trace sets from noisy hand drawings requires design choices from the deep learning and computer vision toolkits (Section~\ref{neuralNetworkSection}); (2) Discovering good programs requires solving a difficult combinatorial search problem, because the programs are often long and complicated (e.g., 9 lines of code, with nested loops and conditionals). We give a generic framework for learning a \emph{search policy} that quickly guides program synthesizers toward the target programs.

@@

\subsection{Generalizing to real hand drawings}\label{generalizingTheHandDrawings}
%% \begin{wrapfigure}{R}{6cm}
%% \centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
%%     \subcaption{}
%%   \end{minipage}\\
%%    \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
%%     \subcaption{}
%%   \end{minipage}%
%%   \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
%%     \subcaption{}
%%   \end{minipage}%
%%     \caption{(a): hand drawing. (b): Rendering of the trace set our model infers for (a). (c): noisy rendering of (b).}\label{handDrawingExamples}
%% \end{wrapfigure}

%A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
 We trained the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images.
We designed this noise process to introduce the kinds of variations found in hand drawings (%% Fig.~\ref{handDrawingExamples}; 
see supplement for details).
